---
title: "Assignment 1"
author: "Tianchun Xue"
date: "2/6/2022"
output: github_document
---

# Load library
```{r}
library(tidyverse)
library(dplyr)
library(titanic)
library(ggplot2)
library(scales)
```

# Data input and organization
I will use "titanic_trian" dataset from the 'titanic' package to do the following analysis.

In this section, I will calculate the survival rate based on different genders.
```{r}
glimpse(titanic_train)
gender_survive <- titanic_train %>%
  group_by(Sex) %>%
  summarise(Survived.count = sum(Survived))  %>%
  mutate(Total.count = table(titanic_train$Sex)) %>%
  mutate(Survival.rate = Survived.count/Total.count)
```

```{r}
gender_survive <- as.data.frame(gender_survive)
gender_survive
```
From the table, we can know that 233 female passengers survived out of all 314 female passengers, and only 109 male passengers survived out of all 577 male passengers.

# Data visualization
I will visualize the survival rate by gender by "ggplot2"

First, I will convert "integer" into "factor", for later filling the gender groups with different survival states.
```{r}
titanic_train$Survived <- as.factor(titanic_train$Survived)
```

Then, I will generate a bar plot to show the survival rates of different gender.
```{r}
ggplot(data= titanic_train,aes(x=Sex, fill=Survived))+
  geom_bar()+
  scale_fill_brewer(palette = 'Paired')+
  annotate(geom="text", x= 1, y=250, label=percent(gender_survive[1,4]),
              color="white")+
  annotate(geom="text", x= 2, y=130, label=percent(gender_survive[2,4]),
              color="white")+
  labs(y = "Number of Passengers", title = "Survival Rate by Gender")+
  theme_classic()
```

Here, "0" of survival states refers to death, and "1" means survival. We can see the x-axis contains two groups, female and male. And the y-axis is the number of passengers. There are more male passengers than female passengers, but the survival rate of male passengers (19%) is much lower than that of female passengers (74%).

